Plant species traits and growth rates: meta-analysis shows correlations change with plant size as predicted

### 2015-05-08 MS.tex
add * metanalyses file

This study is the first one of an upcoming series of theoritical articles and empirical studies performed by the authors on the same thematic: the effect of plant size on plant strategies and functional traits.

>>>>

This study is the first one of an upcoming series of theoritical and empirical studies performed by the authors on the same thematic: the effect of plant size on plant strategies and functional traits.
